The Chemistry Development Kit (CDK) \cdkversion{}: atom typing, depiction, molecular formulas, and substructure searching

### 2017-04-27 article.tex
More citations for performance improvements.

The most significant functional change here is that the SMILES parser automatically 
locates the positions of double bonds in de-localised aromatic systems (Kekulisation).
If this invariant cannot be met the SMILES is rejected as invalid. It is 
possible to override this check but this is strongly discouraged as rejected
molecules do not have a fixed formula or tautomer.

@@

CDK \cdkversion{} includes large improvements to algorithm
efficiency. This is emphasised in the systematic benchmark
of MACCS-like 166 key generation (Table~5). The efficiency improvements
are a combination of optimising data structures and key molecule processing
algorithms (e.g. kekulisation and aromaticity) needed before a SMARTS
match can be run.

>>>>

The most significant functional change here is that the SMILES parser 
automatically locates the positions of double bonds in de-localised aromatic 
systems (Kekulisation). If this invariant cannot be met the SMILES is rejected 
as invalid. It is possible to override this check but this is strongly 
discouraged as rejected molecules do not have a fixed formula or tautomer~\cite{May2015}.

@@

CDK \cdkversion{} includes large improvements to algorithm
efficiency. This is emphasised in the systematic benchmark
of MACCS-like 166 key generation (Table~5). The efficiency improvements
are a combination of optimising data structures and key molecule processing
algorithms (e.g. kekulisation and aromaticity) needed before a SMARTS
match can be run~\cite{MayBlog2013a,MayBlog2013b,May2015}.
